---
title: "Playing with dirichletprocess"
output:
  pdf_document: default
---

```{r setup, echo=FALSE}
require('dirichletprocess')
require('mvtnorm')
require('foreach')
options(digits=3)
set.seed(222)
```
# Questions on `clusterParameters`

```{r dp}
## Generate 10 datapoints on 2D data space from two multinormals:
## one centred at (-1,-1), the other at (1,1),
## with sd = 0.1
datasize <- 10
y <- matrix(rnorm(n=2*datasize, mean=c(-1,-1,1,1), sd=0.1), nrow=datasize, ncol=2, byrow=TRUE)
y

## Create Dirichlet-process object, multinormal mixture:
dp <- DirichletProcessMvnormal(y)

## This object has clusterParameters, with specific values:
dp$clusterParameters
```

**Question**: where do the `clusterParameters` in the initial
Dirichlet-process object come from? Can they be considered prior samples of
the $\theta$s, rather than posterior?


```{r}
## Fit the first Dirichlet-process, save the result under a new name:
fitdp <- Fit(dp, its=1000, progressBar=FALSE)
```

The parameters in the first sample in the fitted object seem to be equal to
the `clusterParameters` in the initial object:

```{r}
fitdp$clusterParametersChain[[1]]
```

**Question**: in general, the `clusterParameters` of a fitted object are
effectively the last samples of the Monte Carlo chain. Is this correct?



# LikelihoodDP

This actually gives the matrix of probability densities of the data
conditional on the `clusterParameters` (or equivalently the likelihood of
the `clusterParameters` in view of the data)
$$
\bigl(\mathrm{p}(y_i \rvert \theta_j, \text{\small
hyperparameters})
\bigr)_{ij}
$$
as can be seen by an explicit calculation with `dmvnorm`:

```{r}
## with LikelihoodDP
LikelihoodDP(fitdp)

## with dmvnorm
unname(foreach(i=1:datasize, .combine='rbind') %:% # iterate over data
       foreach(j=1:datasize, .combine='cbind') %do% { #iterate over params
           dmvnorm(x=y[i,],
                   mean=fitdp$clusterParameters$mu[,,fitdp$clusterLabels[j]],
                   sigma=fitdp$clusterParameters$sig[,,fitdp$clusterLabels[j]],
                   checkSymmetry=FALSE, log=FALSE)
       })
```

# Posterior predictive in conjugate multinormal case





question on `PosteriorClusters`:
where are they drawn from?
can they be used to draw from the prior?
They also work in case of unfitted object: where are they drawn from?

What does `ClusterLabelPredict` do?

How do I draw prior probabilities from the process?

How to update the hyperparameters?

How to have a fixed alpha?

not clear what happens with `ClusterParameterUpdate` and
`ClusterComponentUpdate`: they don't save the new samples in the chain?

where are `weights` for the conjugate multinormal case?

check if g0Priors works

what does "initialize" mean?

`$weights` from page 15 is actually missing

what is `mhDraws`?

faster using directly
`UpdateAlpha(ClusterParameterUpdate(ClusterComponentUpdate(...)))`

